---
title: "Wodlist and concordancing: Lexical graduation in the word 'mito' in YouTube Users Comments"
author: "| Rodrigo Esteves de Lima-Lopes \n| State University of Campinas | rll307@unicamp.br\n| Carolina Palma de Sousa Arruda \n| State University of Campinas \n| carolpalma203@gmail.com"
output: 
  pdf_document:
    number_sections: yes
    toc: yes
    keep_md: true
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

We are going to need the following packages for making a simple wordlist:

```{r packs, eval=FALSE}
library(tidytext)
library(tidyr)
library(dplyr)
library(quanteda)
```

# Cleaning and processing the wordlist

First we will extract the comments from the original data frame

```{r ex, eval=FALSE}
string.comments <- as.character(comments$textOriginal)
```

Next step is to clean numbers and special characters

```{r clean, eval=FALSE}
string.comments <-str_replace_all(string.comments, "[^[:alnum:]]", " ")
```

We are going to use a list of stopwords provided by the package `quanteda`, so no need to import. Probably some users names will pop up, you add them to the list.

```{r stop,eval=FALSE}
my.stopwords <- data.frame(stopwords("pt"))
colnames(my.stopwords)<-"words"
```

Now let us create a data frame so we can process the wordlist.

```{r dataframe, eval=FALSE}
geral.list.df <- data.frame(text = string.comments, stringsAsFactors = F)
colnames(geral.list.df) <- "text"
```

Now we make the wordlist *per se*:

```{r wordlist, eval=FALSE}
geral.list.df <- geral.list.df %>%
  unnest_tokens(word, text, to_lower= FALSE) %>%
  count(word, sort = TRUE) %>%
  anti_join(my.stopwords)%>%
  mutate((freq = n / sum(n))*100) %>% 
  arrange(desc(n))
colnames(geral.list.df)<-c('word','n','freq')

```

# Concordancing

I would suggest `quanteda`'s `kwic` command. It simplifies a lot the concondancing process. Please, substitute the term **word** by you research interest.

```{r conc, eval=FALSE}
corpus.comments <-corpus(comments,text_field = 'textOriginal')
View(kwic(corpus.comments, pattern = "WORD",case_insensitive=FALSE))
```
